---
title: "Data collection with the BSBT Interface"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data collection with the BSBT Interface}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The [BSBT-Interface](https://github.com/BPerrat/BSBT-Interface) provides an easy way to collect comparative judgement data. The interface constructs a SQLite database with the raw data, including which users knew which areas, user information, and a table of comparative judgments. In this vignette, we will use the BSBT model to analyse the comparative judgement data

# Set up database connection
First, we need to connect to the database. This is done using the following commands. 
```{r connections}
library(RSQLite)
library(BSBT)
bsbt.connection   <- dbConnect(RSQLite::SQLite(), "~/Desktop/test.db")
comparisons       <- dbReadTable(bsbt.connection, "rankings")
dbListTables(bsbt.connection) #available tables
```

# Data processing and quality control
The comparison table contains each comparisons made in the survey, its ID number, the ID number of the user who made it, the time it was made, the winner and loser of the comparison, and if the was rejudged. Some of our example data is 
```{r}
head(comparisons)
```
There are a number of quality control measures that need to be carried out before the data is analysed. All comparisons which have been rejudged must be removed from the data set, this means a user has decided they made a mistake and would like to carry out that comparisons again. To do this, we remove any comparisons which have a flag in the rejudged column. 
```{r}
comparisons <- comparisons[comparisons$rejudged == 0, ]
```
It may be worth investigating users who have rejudged many of their comparisons. We may also need to investigate the time the users took to carry out each comparisons, removing users who spend too short a time comparing areas. Finally, we can remove users who have withdrawn from the survey or we suspect are not making valid comparisons. For example, to remove user 2, we call
```{r}
comparisons <- comparisons[-which(comparisons$user_id == 2), ]
```

To use with the `BSBT` package, we need to transform the table into a matrix, where element $w_{ij}$ contains the number of times area $i$ was chosen over area $j$. This can be done by calling
```{r}
win.matrix <- comparisons_to_matrix(452, comparisons[, 4:5])
```


# Data analysis with the BSBT R package
After the data has been processed, we can analyse the data using the BSBT R package. Detailed information about the various modelling approaches and technical details about the MCMC framework can be found in [Seymour et. al. (2021)](https://arxiv.org/abs/2010.14128). We must first construct the prior distribution covariance matrix, which contains the spatial structure of the areas. Then we feed this matrix and the processed data into the MCMC function, which infers the quality of each area. The covariance matrix function requires the adjacency matrix from the shape files. The can be done using the `spdep` package, the `surveillance` package using GIS software, such as QGIS. In this example, we use the adjacency matrix of the 452 subwards in Dar es Salaam, Tanzania. 
```
data("dar.adj.matrix")
k            <- constrained_adjacency_covariance_function(dar.adj.matrix, type = "matrix", hyperparameters = c(1), linear.combination = rep(1, 452), linear.constraint = 0)
mcmc.output  <- run_mcmc(n.iter = 1500000, delta = 0.01, k, win.matrix, f.initial =  rep(0, 452), alpha = TRUE)
```
The MCMC algorithm may take several hours to run. To include the posterior median estimates for the quality of each area in the data base, call
```
N                  <- 452 #number of areas
burn.in            <- 500000 #burn-in period 
mean.deprivation   <- apply(mcmc.output$f[-c(1:burn.in), ], 2, mean)
quality            <- data.frame("area_id" = 1:N, "quality" = mean.deprivation)
dbCreateTable(bsbt.connection, "quality", quality)
dbDisconnect(bsbt.connection) #clean up
```




